---
title: "02_script_for_plots"
output: html_document
date: "2024-01-10"
---
# Scatterplots
## load data
```{r }
library(readxl)
library(dplyr)
library(openxlsx)

file_path <- "../01_data/SUBSET_BDI.xlsx"
SUBSET_BDI <- read.xlsx(file_path)  %>% unique()

file_path <- "../01_data/SUBSET_CESD.xlsx"
SUBSET_CESD <- read.xlsx(file_path) %>% unique()

file_path <- "../01_data/SUBSET_HADS.xlsx"
SUBSET_HADS <- read.xlsx(file_path) %>% unique()

file_path <- "../01_data/SUBSET_PHQ.xlsx"
SUBSET_PHQ <- read.xlsx(file_path) %>% unique()

file_path <- "../01_data/SUBSET_PROMIS.xlsx"
SUBSET_PROMIS <- read.xlsx(file_path) %>% unique()

```

# Felix' Code

## Scatter und Bland-Altmann Plots

```{r }
library(Hmisc)

BDIxCESD = inner_join(SUBSET_BDI, SUBSET_CESD, by = c("Study", "Variable")) %>% unique()
BDIxHADS <- inner_join(SUBSET_BDI, SUBSET_HADS, by = c("Study", "Variable")) %>%unique()
BDIxPHQ <- inner_join(SUBSET_BDI, SUBSET_PHQ, by = c("Study", "Variable")) %>%unique()
BDIxPROMIS <- inner_join(SUBSET_BDI, SUBSET_PROMIS, by = c("Study", "Variable")) %>%unique()
CESDxHADS <- inner_join(SUBSET_CESD, SUBSET_HADS, by = c("Study", "Variable")) %>%unique()
CESDxPHQ <- inner_join(SUBSET_CESD, SUBSET_PHQ, by = c("Study", "Variable")) %>%unique()
CESDxPROMIS <- inner_join(SUBSET_CESD, SUBSET_PROMIS, by = c("Study", "Variable")) %>%unique()
HADSxPHQ <- inner_join(SUBSET_HADS, SUBSET_PHQ, by = c("Study", "Variable")) %>%unique()
HADSxPROMIS <- inner_join(SUBSET_HADS, SUBSET_PROMIS, by = c("Study", "Variable")) %>%unique()
PHQxPROMIS <- inner_join(SUBSET_PHQ, SUBSET_PROMIS, by = c("Study", "Variable"))%>%unique()


results = list(BDIxCESD, BDIxHADS, BDIxPHQ, 
BDIxPROMIS, CESDxHADS, CESDxPHQ, CESDxPROMIS, HADSxPHQ, 
HADSxPROMIS, PHQxPROMIS)
names(results) =  c("BDIxCESD", "BDIxHADS", "BDIxPHQ", 
"BDIxPROMIS", "CESDxHADS", "CESDxPHQ", "CESDxPROMIS", "HADSxPHQ", 
"HADSxPROMIS", "PHQxPROMIS")

results$BDIxPROMIS$PROMIS_PROMIS.Skala = results$BDIxPROMIS$PROMIS

results2 = lapply(names(results), function(x){
results[[x]]$measure_1 = strsplit(x, "x")[[1]][1]
results[[x]]$measure_2 = strsplit(x, "x")[[1]][2]
results[[x]]$value_1 = results[[x]][, grep("PROMIS", names(results[[x]]))[1]]
results[[x]]$value_2 =  results[[x]][, grep("PROMIS", names(results[[x]]))[2]]
results[[x]]$groupsize = results[[x]][,"groupsize.x"]
results[[x]][, c("Study", "Variable", "measure_1", "measure_2", "value_1", "value_2", "groupsize")]
})

str(results2)
results3 = bind_rows(results2)
library(ggplot2)
results3$groupsize = as.numeric(results3$groupsize)

ggplot(results3, aes(x = value_1, value_2)) + geom_point() + facet_grid(measure_1 ~ measure_2) + geom_abline() + geom_smooth()
ggplot(results3, aes(x = value_1, value_2)) + geom_point(aes(size = groupsize)) + facet_grid(measure_1 ~ measure_2) + geom_abline() 

results3$m = (results3$value_1 + results3$value_2)/2
results3$d = (results3$value_1 - results3$value_2)

ggplot(results3, aes(x = m, y = d)) + geom_point()+ facet_grid(measure_1 ~ measure_2)

results4 = results3 %>% group_by(measure_1, measure_2) %>% summarise(mean1 = mean(d), wgt_mean = wtd.mean(d, w = groupsize, na.rm = T),
                                                                     sd = sd(d), wtd_sd = sqrt(wtd.var(d, w = groupsize)),
                                                                     lo = mean1-1.96*sd, hi = mean1+1.96*sd,
                                                                     wtd_lo = wgt_mean-1.96*wtd_sd, wtd_hi = wgt_mean+1.96*wtd_sd)

ggplot(results3, aes(x = m, y = d)) + geom_point()+ facet_grid(measure_1 ~ measure_2) + 
  geom_hline(data = results4, aes(yintercept = mean1)) + 
  geom_hline(data = results4, aes(yintercept = lo), linetype = 2) +
  geom_hline(data = results4, aes(yintercept = hi), linetype = 2) +
  geom_text(data = results4, aes(x = 30, y = mean1, label = sprintf("%.1f", mean1)), vjust = -.2) +
  geom_text(data = results4, aes(x = 30, y = lo, label = sprintf("%.1f", lo)), vjust = -.2) +
  geom_text(data = results4, aes(x = 30, y = hi, label = sprintf("%.1f", hi)), vjust = -.2) +
  coord_cartesian(xlim = c(20,80)) +
  labs(title = "Unweighted")

ggplot(results3, aes(x = m, y = d)) + geom_point()+ facet_grid(measure_1 ~ measure_2) + 
  geom_hline(data = results4, aes(yintercept = wgt_mean)) + 
  geom_hline(data = results4, aes(yintercept = wtd_lo), linetype = 2) +
  geom_hline(data = results4, aes(yintercept = wtd_hi), linetype = 2) +
  labs(title = "Weighted")

```

## mean of (absolute) d 
```{r }

d_absolute <- abs(results3$d)
d_absolute_mean <- mean(d_absolute)
summary(d_absolute)
sd(d_absolute)

#mean of d
d <- results3$d
d_mean <- mean(d)
summary(d)
sd(d)
```

## linear mixed model estimates

Wir möchten die Differenz i in Gruppe j aufteilen in Anteile, die auf Unterschiede der jeweiligen Fragebogenkombination j zurückgehen und Unterschiede die auch innerhalb der Fragebogenkombination noch zwischen einzelnen Studien i bestehen. 

Es ist ein Mixed model weil wir von festen und von random effects (pro Studie unterscheiden sich die Differenzen) ausgehen. 


```{r }
#install.packages("lme4")
#install.packages("lmerTest")
#install.packages("Matrix")

library(lme4)
library(lmerTest)
library(Matrix)

interceptonlymodel <- lmer(formula = d ~ 1 + (1|Study), weights=groupsize,
                           data = results3)

## hier weiter mit https://shiny.psy.lmu.de/tutorials/lineare-gemischte-modelle-linear-mixed-models---lmm.html#intro und notion 
summary(interceptonlymodel)

#install.packages("sjPlot")
library(sjPlot)
plot_model(model = interceptonlymodel, type = 'pred', terms = 'Study')

```

### Hinzufügen eines Level-1 Prädiktors
Wir wollen herausfinden, woran es liegen könnte, dass die Studien unterschiedliche Differenzen haben.

Hypothese 1: Die Differenz hängt mit der Fragebogenkombination zusammen.


```{r }
# install.packages("knitr")
# install.packages("kableExtra")

library(knitr)
library(kableExtra)


results3$questionnaire_pair = paste(results3$measure_1, results3$measure_2)
results3$questionnaire_pair = factor(paste(results3$measure_1, results3$measure_2))

interceptonlymodel <- lmer(formula = d ~ 1 + questionnaire_pair + (1|Study), weights = groupsize, data = results3)
summary(interceptonlymodel)
lmerTest::ls_means(interceptonlymodel, which = "questionnaire_pair")

```

# ANOVA

H0 wird abgelehnt -> es gibt signifikante Unterschiede zwischne den Differenzen der Fragebögen
```{r }

anova_result <- aov(d ~ questionnaire_pair, data = results3)
summary(anova_result)

```
# Forest plot 

```{r }

## load up the packages we will need: 
library(tidyverse)
library(gt)
library(patchwork)

library(ggplot2)

# Data
data <- data.frame(
  Comparison = c("BDI x CESD (7 studies)", "BDI x HADS (9 studies)", "BDI x PHQ (20 studies)", "BDI x PROMIS (1 study)",
                 "CESD x HADS (14 studies)", "CESD x PHQ (9 studies)", "CESD x PROMIS (1 study)",
                 "HADS x PHQ (19 studies)", "HADS x PROMIS (1 study)", "PHQ x PROMIS (6 studies)"),
  Estimate = c(-2.97582, 1.52532, -0.78826, 1.79057, 2.85519,
               1.46963, 5.45416, -2.47907, -2.65198, 5.30093),
  Std.Error = c(1.31949, 0.97459, 0.68534, 2.98016, 0.82313,
                0.89610, 1.29958, 0.70739, 3.06720, 1.03198),
  lower = c(-5.59149, -0.40445, -2.15921, -4.21102, 1.20904,
            -0.32298, 2.89030, -3.89421, -8.80756, 3.25347),
  upper = c(-0.36015, 3.45508, 0.58269, 7.79216, 4.50134,
            3.26224, 8.01801, -1.06393, 3.50360, 7.34839),
  p.value = c(0.0261462, 0.1202153, 0.2546478, 0.5509542,
               0.0009684, 0.1062524, 4.193e-05, 0.0008742, 0.3912369, 1.388e-06)
)


# Order the data by Estimate
data <- data[order(data$Estimate), ]

# Forest plot
plot <- ggplot(data, aes(x = Estimate, y = Comparison)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  scale_x_continuous(limits = c(-10, 10)) +
  theme_minimal() +
  labs(
    title = "Forest Plot",
    subtitle = "Comparison of Questionnaires",
    x = "Estimate",
    y = "Comparison",
    caption = "Error bars represent 95% confidence intervals"
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )


# Define the file path
file_path <- "../04_results/forest_plot.png"

# Save the plot
ggsave(file_path, plot, width = 10, height = 8)


plot
```

# save table 2
```{r }


```


## Scatterplots einzeln über alle Fragebogenkombinationen

```{r }
library(ggplot2)
#install.packages("hrbrthemes")
library(hrbrthemes)
```


#### BDIxCESD
```{r }
BDIxCESD$groupsize.y <- as.numeric(as.character(BDIxCESD$groupsize.y)) 
BDIxCESD_plot<- ggplot(BDIxCESD, aes(x = `BDI.-.PROMIS.Skala`, y = `CESD.-.PROMIS.Skala`)) + 
  geom_point(aes(size = groupsize.y)) +
  geom_smooth(method = "lm", color = "red", fill = "#69b3a2", se = TRUE) +
  xlim(40, 90) +
  ylim(40, 90) +
  labs(size = "Gruppengröße") +  # Hier wird der Name der Punktgröße geändert
  theme_ipsum()
```

#### BDIxHADS
```{r }
BDIxHADS$groupsize.y <- as.numeric(as.character(BDIxHADS$groupsize.y))  
BDIxHADS_plot<- ggplot(BDIxHADS, aes(x = `BDI.-.PROMIS.Skala`, y = `HADS.-.PROMIS.Skala`)) + 
  geom_point(aes(size = groupsize.y)) +
  geom_smooth(method = "lm", color = "red", fill = "#69b3a2", se = TRUE) +
  xlim(40, 90) +
  ylim(40, 90) +
  labs(size = "Gruppengröße") +  # Hier wird der Name der Punktgröße geändert
  theme_ipsum()
```
  
#### BDIxPHQ
```{r }
BDIxPHQ$groupsize.y <- as.numeric(as.character(BDIxPHQ$groupsize.y))  
BDIxPHQ_plot<- ggplot(BDIxPHQ, aes(x = `BDI.-.PROMIS.Skala`, y = `PHQ.-.PROMIS.Skala`)) + 
  geom_point(aes(size = groupsize.y)) +
  geom_smooth(method = "lm", color = "red", fill = "#69b3a2", se = TRUE) +
  xlim(40, 90) +
  ylim(40, 90) +
  labs(size = "Gruppengröße") + 
  theme_ipsum()
```

#### BDIxPROMIS
```{r }
BDIxPROMIS$groupsize.y <- as.numeric(as.character(BDIxPROMIS$groupsize.y))  
BDIxPROMIS_plot <- ggplot(BDIxPROMIS, aes(x = `BDI.-.PROMIS.Skala`, y = `PROMIS`)) + 
  geom_point(aes(size = groupsize.y)) +
  geom_smooth(method = "lm", color = "red", fill = "#69b3a2", se = TRUE) +
  xlim(40, 90) +
  ylim(40, 90) +
  labs(size = "Gruppengröße") +  
  theme_ipsum()
```

#### CESDxHADS
```{r }
CESDxHADS$groupsize.y <- as.numeric(as.character(CESDxHADS$groupsize.y))  
CESDxHADS_plot <- ggplot(CESDxHADS, aes(x = `CESD.-.PROMIS.Skala`, y = `HADS.-.PROMIS.Skala`)) + 
  geom_point(aes(size = groupsize.y)) +
  geom_smooth(method = "lm", color = "red", fill = "#69b3a2", se = TRUE) +
  xlim(40, 90) +
  ylim(40, 90) +
  labs(size = "Gruppengröße") +
  theme_ipsum()
```

#### CESDxPHQ
```{r }
CESDxPHQ$groupsize.y <- as.numeric(as.character(CESDxPHQ$groupsize.y))  
CESDxPHQ_plot <- ggplot(CESDxPHQ, aes(x = `CESD.-.PROMIS.Skala`, y = `PHQ.-.PROMIS.Skala`)) + 
  geom_point(aes(size = groupsize.y)) +
  geom_smooth(method = "lm", color = "red", fill = "#69b3a2", se = TRUE) +
  xlim(40, 90) +
  ylim(40, 90) +
  labs(size = "Gruppengröße") +
  theme_ipsum()
```

#### PHQxPROMIS
```{r }
PHQxPROMIS$groupsize.y <- as.numeric(as.character(PHQxPROMIS$groupsize.y))  
PHQxPROMIS_plot <- ggplot(PHQxPROMIS, aes(x = `PHQ.-.PROMIS.Skala`, y = `PROMIS`)) + 
  geom_point(aes(size = groupsize.y)) +
  geom_smooth(method = "lm", color = "red", fill = "#69b3a2", se = TRUE) +
  xlim(40, 90) +
  ylim(40, 90) +
  labs(size = "Gruppengröße") +
  theme_ipsum()
```

#### HADSxPHQ
```{r }
HADSxPHQ$groupsize.y <- as.numeric(as.character(HADSxPHQ$groupsize.y))  
HADSxPHQ_plot <- ggplot(HADSxPHQ, aes(x = `HADS.-.PROMIS.Skala`, y = `PHQ.-.PROMIS.Skala`)) + 
  geom_point(aes(size = groupsize.y)) +
  geom_smooth(method = "lm", color = "red", fill = "#69b3a2", se = TRUE) +
  xlim(40, 90) +
  ylim(40, 90) +
  labs(size = "Gruppengröße") +
  theme_ipsum()
```

### Facetted Plot als Grid erstellen
```{r }
# einen Datensatz aus allen erstellen mit Wert 1 und Wert 2 und einer Zeile der Fragebogenkombination 

BDIxCESD_short <- BDIxCESD %>%
  mutate(`Wert 1` = `BDI.-.PROMIS.Skala`,
         `Wert 2` = `CESD.-.PROMIS.Skala`,
         `Fragebogenkombination` = "BDIxCESD")


BDIxHADS_short <- BDIxHADS %>%
  mutate(`Wert 1` = `BDI.-.PROMIS.Skala`,
         `Wert 2` = `HADS.-.PROMIS.Skala`,
         `Fragebogenkombination` = "BDIxHADS")


BDIxPHQ_short <- BDIxPHQ %>%
  mutate(`Wert 1` = `BDI.-.PROMIS.Skala`,
         `Wert 2` = `PHQ.-.PROMIS.Skala`,
         `Fragebogenkombination` = "BDIxPHQ")


BDIxPROMIS_short <- BDIxPROMIS %>%
  mutate(`Wert 1` = `BDI.-.PROMIS.Skala`,
         `Wert 2` = `-.PROMIS.Skala`,
         `Fragebogenkombination` = "BDIxPROMIS")


CESDxHADS_short <- CESDxHADS %>%
  mutate(`Wert 1` = `CESD.-.PROMIS.Skala`,
         `Wert 2` = `HADS.-.PROMIS.Skala`,
         `Fragebogenkombination` = "CESDxHADS")


CESDxPHQ_short  <- CESDxPHQ %>%
  mutate(`Wert 1` = `CESD.-.PROMIS.Skala`,
         `Wert 2` = `PHQ.-.PROMIS.Skala`,
         `Fragebogenkombination` = "CESDxPHQ")


CESDxPROMIS_short  <- CESDxPROMIS %>%
  mutate(`Wert 1` = `CESD.-.PROMIS.Skala`,
         `Wert 2` = `-.PROMIS.Skala`,
         `Fragebogenkombination` = "CESDxPROMIS")


HADSxPHQ_short  <- HADSxPHQ %>%
  mutate(`Wert 1` = `HADS.-.PROMIS.Skala`,
         `Wert 2` = `PHQ.-.PROMIS.Skala`,
         `Fragebogenkombination` = "HADSxPHQ")


HADSxPROMIS_short <- HADSxPROMIS %>%
  mutate(`Wert 1` = `HADS.-.PROMIS.Skala`,
         `Wert 2` = `-.PROMIS.Skala`,
         `Fragebogenkombination` = "HADSxPROMIS")


PHQxPROMIS_short <- PHQxPROMIS %>%
  mutate(`Wert 1` = `PHQ.-.PROMIS.Skala`,
         `Wert 2` = `-.PROMIS.Skala`,
         `Fragebogenkombination` = "PHQxPROMIS")

# datensätze verbinden, um sie als faceted plot aus einer Tabelle plotten zu können

BDIxCESD_short_selected <- BDIxCESD_short %>%
  select("Wert 1", "Wert 2", "Fragebogenkombination", "groupsize.y")

BDIxHADS_short_selected <- BDIxHADS_short %>%
  select("Wert 1", "Wert 2", "Fragebogenkombination", "groupsize.y")

BDIxPHQ_short_selected <- BDIxPHQ_short %>%
  select("Wert 1", "Wert 2", "Fragebogenkombination", "groupsize.y")

BDIxPROMIS_short_selected <- BDIxPROMIS_short %>%
  select("Wert 1", "Wert 2", "Fragebogenkombination", "groupsize.y")

CESDxHADS_short_selected <- CESDxHADS_short %>%
  select("Wert 1", "Wert 2", "Fragebogenkombination", "groupsize.y")

CESDxPHQ_short_selected <- CESDxPHQ_short %>%
  select("Wert 1", "Wert 2", "Fragebogenkombination", "groupsize.y")

PHQxPROMIS_short_selected <- PHQxPROMIS_short %>%
  select("Wert 1", "Wert 2", "Fragebogenkombination", "groupsize.y")

HADSxPHQ_short_selected <- HADSxPHQ_short %>%
  select("Wert 1", "Wert 2", "Fragebogenkombination", "groupsize.y")



# Datensätze untereinander verbinden (join)
verbundener_datensatz <- bind_rows(
  BDIxHADS_short_selected,
  BDIxCESD_short_selected,
  BDIxPHQ_short_selected,
  BDIxPROMIS_short_selected,
  CESDxHADS_short_selected,
  CESDxPHQ_short_selected,
  PHQxPROMIS_short_selected,
  HADSxPHQ_short_selected
)

# Ersetze "nicht berichtet (!)" durch NA in allen Spalten
verbundener_datensatz <- verbundener_datensatz %>%
  mutate_all(~ ifelse(. == "nicht berichtet (!)", NA, .)) %>%
  rename(Wert1 = "Wert 1", Wert2 = "Wert 2")

# ggplot erstellen


sp <- ggplot(data = verbundener_datensatz, aes(x = Wert2, y = Wert1)) +
  geom_point(aes(size = ifelse(is.na(groupsize.y), 100, groupsize.y), color = ifelse(is.na(groupsize.y), "blue", "black"))) +
  geom_smooth(method = "lm", color = "red", size = 0.5, fill = "#69b3a2", se = TRUE) +
  labs(size = "Groupsize") +
  scale_size_continuous(range = c(0, 5), breaks = seq(0, 4000, by = 1000)) +
  scale_color_identity() +
  xlim(40, 90) +
  ylim(40, 90) +
  labs(x = "First Value of combination", y = "Second Value of combination")



sp

faceted_scatterplot <- sp + facet_wrap( ~ Fragebogenkombination, ncol = 3)

file_path <- "../04_results/faceted_scatterplot.png"
ggsave(file_path, faceted_scatterplot, width = 10, height = 6, units = "in")




```


# Blant Altman Plots
## Version 1 mit blandr.draw Funktion
### Blant Altman Plot einzeln 
```{r }
#install.packages("blandr")
library(blandr)

#BDIxCESD
BDIxCESD_BA_plot <- blandr.draw(BDIxCESD$'BDI.-.PROMIS.Skala', BDIxCESD$'CESD.-.PROMIS.Skala') +
  theme(text = element_text(size = 6)) +
  labs(title = "BDIxCESD") +
  xlim(40, 80) +
  ylim(-15, 25)

# BDIxHADS
BDIxHADS_BA_plot <- blandr.draw(BDIxHADS$'BDI.-.PROMIS.Skala', BDIxHADS$'HADS.-.PROMIS.Skala') +
  theme(text = element_text(size = 6)) +
  labs(title = "BDIxHADS") +
  xlim(40, 80) +
  ylim(-15, 25)

# BDIxPHQ
BDIxPHQ_BA_plot <- blandr.draw(BDIxPHQ$'BDI.-.PROMIS.Skala', BDIxPHQ$'PHQ.-.PROMIS.Skala') +
  theme(text = element_text(size = 6)) +
  labs(title = "BDIxPHQ") +
  xlim(40, 80) +
  ylim(-15, 25)

# BDIxPROMIS
BDIxPROMIS_BA_plot <- blandr.draw(BDIxPROMIS$'BDI.-.PROMIS.Skala', BDIxPROMIS$'-.PROMIS.Skala') +
  theme(text = element_text(size = 6)) +
  labs(title = "BDIxPROMIS") +
  xlim(40, 80) +
  ylim(-15, 25)


# CESDxHADS
CESDxHADS_BA_plot <- blandr.draw(CESDxHADS$'CESD.-.PROMIS.Skala', CESDxHADS$'HADS.-.PROMIS.Skala') +
  theme(text = element_text(size = 6)) +
  labs(title = "CESDxHADS") +
  xlim(40, 80) +
  ylim(-15, 25)

# CESDxPHQ
CESDxPHQ_BA_plot <- blandr.draw(CESDxPHQ$'CESD.-.PROMIS.Skala', CESDxPHQ$'PHQ.-.PROMIS.Skala') +
  theme(text = element_text(size = 6)) +
  labs(title = "CESDxPHQ") +
  xlim(40, 80) +
  ylim(-15, 25)

# CESDxPROMIS
#CESDxPROMIS_BA_plot <- blandr.draw(CESDxPROMIS$'CESD.-.PROMIS.Skala', CESDxPROMIS$'-.PROMIS.Skala') +
#  theme(text = element_text(size = 6)) +
#  labs(title = "CESDxPROMIS") +
#  xlim(40, 80) +
#  ylim(-15, 25)


# HADSxPHQ  
HADSxPHQ_BA_plot <- blandr.draw(HADSxPHQ$'HADS.-.PROMIS.Skala', HADSxPHQ$'PHQ.-.PROMIS.Skala') +
  theme(text = element_text(size = 6)) +
  labs(title = "HADSxPHQ") +
  xlim(40, 80) +
  ylim(-15, 25)

# PHQxPROMIS
PHQxPROMIS_BA_plot <- blandr.draw(PHQxPROMIS$'PHQ.-.PROMIS.Skala', PHQxPROMIS$'-.PROMIS.Skala',
                                  x.plot.mode = 4) +
  theme(text = element_text(size = 6)) +
  labs(title = "PHQxPROMIS") +
  xlim(40, 80) +
  ylim(-15, 25)


```


### Blant Altman Plot alle
```{r }
library(gridExtra)

Blant_plot<- suppressWarnings({
  BDIxCESD_BA_plot <- blandr.draw(BDIxCESD$'BDI.-.PROMIS.Skala', BDIxCESD$'CESD.-.PROMIS.Skala')
  BDIxCESD_BA_plot <- BDIxCESD_BA_plot +
    geom_point(size = 0.1) +
    scale_size(range = c(0.1, 1.0)) +  
    theme(text = element_text(size = 6)) +
    
    labs(title = "BDIxCESD") +
    xlim(40, 80) +
    ylim(-15, 25)

  BDIxHADS_BA_plot 
  BDIxPHQ_BA_plot
  CESDxHADS_BA_plot 
  CESDxPHQ_BA_plot
  PHQxPROMIS_BA_plot
  HADSxPHQ_BA_plot 

  grid.arrange(BDIxCESD_BA_plot, BDIxHADS_BA_plot, BDIxPHQ_BA_plot, CESDxHADS_BA_plot, CESDxPHQ_BA_plot, PHQxPROMIS_BA_plot,HADSxPHQ_BA_plot, nrow = 2)
})


```


## Version 2: händisch Plots bauen um weighted means einbeziehen zu können
### Blant Altman Plots mit weighted means
#### BDIxCESD
```{r }

# der weighted mean ist nur eine Zahl weil er über alle Werte und Weights mittelt:
BDIxCESD$weigh.mean.BDI <- weighted.mean(BDIxCESD$'BDI.-.PROMIS.Skala', BDIxCESD$groupsize.y)
BDIxCESD$weigh.mean.CESD <- weighted.mean(BDIxCESD$'CESD.-.PROMIS.Skala', BDIxCESD$groupsize.y)
BDIxCESD$weigh.diff <- BDIxCESD$weigh.mean.BDI - BDIxCESD$weigh.mean.CESD

#create a new column for average measurement
BDIxCESD$avg <- rowMeans(BDIxCESD[c('BDI.-.PROMIS.Skala', 'CESD.-.PROMIS.Skala')], na.rm = TRUE)

#create a new column for differences
BDIxCESD$diff <- BDIxCESD$'BDI.-.PROMIS.Skala' - BDIxCESD$'CESD.-.PROMIS.Skala'

#find an average difference
mean_diff <- mean(BDIxCESD$diff)
mean_diff_bdixcesd <- mean_diff

#find lower 95% confidence interval limits
lower <- mean_diff - 1.96*sd(BDIxCESD$diff)

# find upper 95% confidence interval limits
upper <- mean_diff + 1.96*sd(BDIxCESD$diff)

# Create the Bland-Altman Plot
library(ggplot2)
BDIxCESD_BA_plot_weighted <- ggplot(BDIxCESD, aes(x = avg, y = diff)) +
  geom_point(size=1) +
  geom_hline(yintercept = mean_diff, linetype="dashed", lwd=0.5) +
  geom_hline(yintercept = lower, color = "red", linetype="dashed") +
  geom_hline(yintercept = upper, color = "red", linetype="dashed") +
  geom_hline(yintercept = 0, color = "blue") +
  ggtitle("BDIxCESD") +
  ylab("Difference Between Instruments") +
  xlab("Average")+
  theme_bw() +
  theme(
    text = element_text(size = 8),  
    axis.title = element_text(size = 6),
    axis.text = element_text(size = 8),
    plot.title = element_text(size = 8) 
  ) +  xlim(40, 80) +
  ylim(-15, 25) 


```


####BDIxHADS
```{r }

# Calculate weighted means
weigh.mean.BDI <- weighted.mean(BDIxHADS$'BDI.-.PROMIS.Skala', BDIxHADS$groupsize.y)
weigh.mean.HADS <- weighted.mean(BDIxHADS$'HADS.-.PROMIS.Skala', BDIxHADS$groupsize.y)
weigh.diff <- weigh.mean.BDI - weigh.mean.HADS

# Create a new column for average measurement
BDIxHADS$avg <- rowMeans(BDIxHADS[c('BDI.-.PROMIS.Skala', 'HADS.-.PROMIS.Skala')], na.rm = TRUE)

# Create a new column for differences
BDIxHADS$diff <- BDIxHADS$'BDI.-.PROMIS.Skala' - BDIxHADS$'HADS.-.PROMIS.Skala'

# Find the average difference
mean_diff <- mean(BDIxHADS$diff)
mean_diff_bdixhads <- mean_diff

# Find lower 95% confidence interval limits
lower <- mean_diff - 1.96 * sd(BDIxHADS$diff)

# Find upper 95% confidence interval limits
upper <- mean_diff + 1.96 * sd(BDIxHADS$diff)

# Create the Bland-Altman Plot
library(ggplot2)
BDIxHADS_BA_plot_weighted <- ggplot(BDIxHADS, aes(x = avg, y = diff)) +
  geom_point(size=1) +
  geom_hline(yintercept = mean_diff, linetype="dashed", lwd=0.5) +
  geom_hline(yintercept = lower, color = "red", linetype="dashed") +
  geom_hline(yintercept = upper, color = "red", linetype="dashed") +
  geom_hline(yintercept = 0, color = "blue") +
  ggtitle("BDIxHADS") +
  ylab("Difference Between Instruments") +
  xlab("Average") +
  theme_bw() +
  theme(
    text = element_text(size = 8),  
    axis.title = element_text(size = 6),
    axis.text = element_text(size = 8),
    plot.title = element_text(size = 8) 
  ) +
  xlim(40, 80) +
  ylim(-15, 25)

```
####BDIxPHQ
```{r }
# Calculate weighted means
weigh.mean.BDI <- weighted.mean(BDIxPHQ$'BDI.-.PROMIS.Skala', BDIxPHQ$groupsize.y)
weigh.mean.PHQ <- weighted.mean(BDIxPHQ$'PHQ.-.PROMIS.Skala', BDIxPHQ$groupsize.y)
weigh.diff <- weigh.mean.BDI - weigh.mean.PHQ

# Create a new column for average measurement
BDIxPHQ$avg <- rowMeans(BDIxPHQ[c('BDI.-.PROMIS.Skala', 'PHQ.-.PROMIS.Skala')], na.rm = TRUE)

# Create a new column for differences
BDIxPHQ$diff <- BDIxPHQ$'BDI.-.PROMIS.Skala' - BDIxPHQ$'PHQ.-.PROMIS.Skala'

# Find the average difference
mean_diff <- mean(BDIxPHQ$diff)
mean_diff_bdixphq <- mean_diff

# Find lower 95% confidence interval limits
lower <- mean_diff - 1.96 * sd(BDIxPHQ$diff)

# Find upper 95% confidence interval limits
upper <- mean_diff + 1.96 * sd(BDIxPHQ$diff)

# Create the Bland-Altman Plot
library(ggplot2)
BDIxPHQ_BA_plot_weighted <- ggplot(BDIxPHQ, aes(x = avg, y = diff)) +
  geom_point(size=1) +
  geom_hline(yintercept = mean_diff, linetype="dashed", lwd=0.5) +
  geom_hline(yintercept = lower, color = "red", linetype="dashed") +
  geom_hline(yintercept = upper, color = "red", linetype="dashed") +
  geom_hline(yintercept = 0, color = "blue") +
  ggtitle("BDIxPHQ") +
  ylab("Difference Between Instruments") +
  xlab("Average") +
  theme_bw() +
  theme(
    text = element_text(size = 8),  
    axis.title = element_text(size = 6),
    axis.text = element_text(size = 8),
    plot.title = element_text(size = 8) 
  ) +
  xlim(40, 80) +
  ylim(-15, 25)

```
####BDIxPROMIS
```{r }

# Assuming your data frame is named BDIxPROMIS

# Calculate weighted means
weigh.mean.BDI <- weighted.mean(BDIxPROMIS$'BDI.-.PROMIS.Skala', BDIxPROMIS$groupsize.y)
weigh.mean.PROMIS <- weighted.mean(BDIxPROMIS$'-.PROMIS', BDIxPROMIS$groupsize.y)
weigh.diff <- weigh.mean.BDI - weigh.mean.PROMIS

# Create a new column for average measurement
BDIxPROMIS$avg <- rowMeans(BDIxPROMIS[c('BDI.-.PROMIS.Skala', '-.PROMIS.Skala')], na.rm = TRUE)

# Create a new column for differences
BDIxPROMIS$diff <- BDIxPROMIS$'BDI.-.PROMIS.Skala' - BDIxPROMIS$'-.PROMIS'

# Find the average difference
mean_diff <- mean(BDIxPROMIS$diff)
mean_diff_bdixpromis <- mean_diff

# Find lower 95% confidence interval limits
lower <- mean_diff - 1.96 * sd(BDIxPROMIS$diff)

# Find upper 95% confidence interval limits
upper <- mean_diff + 1.96 * sd(BDIxPROMIS$diff)

# Create the Bland-Altman Plot
library(ggplot2)
BDIxPROMIS_BA_plot_weighted <- ggplot(BDIxPROMIS, aes(x = avg, y = diff)) +
  geom_point(size=1) +
  geom_hline(yintercept = mean_diff, linetype="dashed", lwd=0.5) +
  geom_hline(yintercept = lower, color = "red", linetype="dashed") +
  geom_hline(yintercept = upper, color = "red", linetype="dashed") +
  geom_hline(yintercept = 0, color = "blue") +
  ggtitle("BDIxPROMIS") +
  ylab("Difference Between Instruments") +
  theme_bw() +
  theme(
    text = element_text(size = 8),  
    axis.title = element_text(size = 6),
    axis.text = element_text(size = 8),
    plot.title = element_text(size = 8) 
  ) +
  xlim(40, 80) +
  ylim(-15, 25)



```


####CESDxHADS
```{r }

# Assuming CESDxHADS contains CESD and HADS scores

# Calculate weighted means
weigh.mean.CESD <- weighted.mean(CESDxHADS$'CESD.-.PROMIS.Skala', CESDxHADS$groupsize.y)
weigh.mean.HADS <- weighted.mean(CESDxHADS$'HADS.-.PROMIS.Skala', CESDxHADS$groupsize.y)
weigh.diff <- weigh.mean.CESD - weigh.mean.HADS

# Create a new column for average measurement
CESDxHADS$avg <- rowMeans(CESDxHADS[c('CESD.-.PROMIS.Skala', 'HADS.-.PROMIS.Skala')], na.rm = TRUE)

# Create a new column for differences
CESDxHADS$diff <- CESDxHADS$'CESD.-.PROMIS.Skala' - CESDxHADS$'HADS.-.PROMIS.Skala'

# Find the average difference
mean_diff <- mean(CESDxHADS$diff)
mean_diff_cesdxhads <- mean_diff

# Find lower 95% confidence interval limits
lower <- mean_diff - 1.96 * sd(CESDxHADS$diff)

# Find upper 95% confidence interval limits
upper <- mean_diff + 1.96 * sd(CESDxHADS$diff)

# Create the Bland-Altman Plot
library(ggplot2)
CESDxHADS_BA_plot_weighted <- ggplot(CESDxHADS, aes(x = avg, y = diff)) +
  geom_point(size=1) +
  geom_hline(yintercept = mean_diff, linetype="dashed", lwd=0.5) +
  geom_hline(yintercept = lower, color = "red", linetype="dashed") +
  geom_hline(yintercept = upper, color = "red", linetype="dashed") +
  geom_hline(yintercept = 0, color = "blue") +
  ggtitle("CESDxHADS") +
  ylab("Difference Between Instruments") +
  xlab("Average") +
  theme_bw() +
  theme(
    text = element_text(size = 8),  
    axis.title = element_text(size = 6),
    axis.text = element_text(size = 8),
    plot.title = element_text(size = 8) 
  ) +
  xlim(40, 80) +
  ylim(-15, 25)


```
####CESDxPHQ
```{r }

# Assuming your data frame is named CESDxPHQ

# Calculate weighted means
weigh.mean.CESD <- weighted.mean(CESDxPHQ$'CESD.-.PROMIS.Skala', CESDxPHQ$groupsize.y)
weigh.mean.PHQ <- weighted.mean(CESDxPHQ$'PHQ.-.PROMIS.Skala', CESDxPHQ$groupsize.y)
weigh.diff <- weigh.mean.CESD - weigh.mean.PHQ

# Create a new column for average measurement
CESDxPHQ$avg <- rowMeans(CESDxPHQ[c('CESD.-.PROMIS.Skala', 'PHQ.-.PROMIS.Skala')], na.rm = TRUE)

# Create a new column for differences
CESDxPHQ$diff <- CESDxPHQ$'CESD.-.PROMIS.Skala' - CESDxPHQ$'PHQ.-.PROMIS.Skala'

# Find the average difference
mean_diff <- mean(CESDxPHQ$diff)
mean_diff_cesdxphq <- mean_diff

# Find lower 95% confidence interval limits
lower <- mean_diff - 1.96 * sd(CESDxPHQ$diff)

# Find upper 95% confidence interval limits
upper <- mean_diff + 1.96 * sd(CESDxPHQ$diff)

# Create the Bland-Altman Plot
library(ggplot2)
CESDxPHQ_BA_plot_weighted <- ggplot(CESDxPHQ, aes(x = avg, y = diff)) +
  geom_point(size=1) +
  geom_hline(yintercept = mean_diff, linetype="dashed", lwd=0.5) +
  geom_hline(yintercept = lower, color = "red", linetype="dashed") +
  geom_hline(yintercept = upper, color = "red", linetype="dashed") +
  geom_hline(yintercept = 0, color = "blue") +
  ggtitle("CESDxPHQ") +
  ylab("Difference Between Instruments") +
  xlab("Average") +
  theme_bw() +
  theme(
    text = element_text(size = 8),  
    axis.title = element_text(size = 6),
    axis.text = element_text(size = 8),
    plot.title = element_text(size = 8) 
  ) +
  xlim(40, 80) +
  ylim(-15, 25)


```
#### PHQxPROMIS
```{r }
# Assuming your data frame is named PHQxPROMIS

# Calculate weighted means
weigh.mean.PHQ <- weighted.mean(PHQxPROMIS$'PHQ.-.PROMIS.Skala', PHQxPROMIS$groupsize.y)
weigh.mean.PROMIS <- weighted.mean(PHQxPROMIS$'-.PROMIS.Skala', PHQxPROMIS$groupsize.y)
weigh.diff <- weigh.mean.PHQ - weigh.mean.PROMIS

# Create a new column for average measurement
PHQxPROMIS$avg <- rowMeans(PHQxPROMIS[c('PHQ.-.PROMIS.Skala', '-.PROMIS.Skala')], na.rm = TRUE)

# Create a new column for differences
PHQxPROMIS$diff <- PHQxPROMIS$'PHQ.-.PROMIS.Skala' - PHQxPROMIS$'-.PROMIS.Skala'

# Find the average difference
mean_diff <- mean(PHQxPROMIS$diff)
mean_diff_phqxpromis <- mean_diff

# Find lower 95% confidence interval limits
lower <- mean_diff - 1.96 * sd(PHQxPROMIS$diff)

# Find upper 95% confidence interval limits
upper <- mean_diff + 1.96 * sd(PHQxPROMIS$diff)

# Create the Bland-Altman Plot
library(ggplot2)
PHQxPROMIS_BA_plot_weighted <- ggplot(PHQxPROMIS, aes(x = avg, y = diff)) +
  geom_point(size=1) +
  geom_hline(yintercept = mean_diff, linetype="dashed", lwd=0.5) +
  geom_hline(yintercept = lower, color = "red", linetype="dashed") +
  geom_hline(yintercept = upper, color = "red", linetype="dashed") +
  geom_hline(yintercept = 0, color = "blue") +
  ggtitle("PHQxPROMIS") +
  ylab("Difference Between Instruments") +
  theme_bw() +
  theme(
    text = element_text(size = 8),  
    axis.title = element_text(size = 6),
    axis.text = element_text(size = 8),
    plot.title = element_text(size = 8) 
  ) +
  xlim(40, 80) +
  ylim(-15, 25)

```
####HADSxPHQ
```{r }
# Assuming your data frame is named HADSxPHQ

# Calculate weighted means
weigh.mean.HADS <- weighted.mean(HADSxPHQ$'HADS.-.PROMIS.Skala', HADSxPHQ$groupsize.y)
weigh.mean.PHQ <- weighted.mean(HADSxPHQ$'PHQ.-.PROMIS.Skala', HADSxPHQ$groupsize.y)
weigh.diff <- weigh.mean.HADS - weigh.mean.PHQ

# Create a new column for average measurement
HADSxPHQ$avg <- rowMeans(HADSxPHQ[c('HADS.-.PROMIS.Skala', 'PHQ.-.PROMIS.Skala')], na.rm = TRUE)

# Create a new column for differences
HADSxPHQ$diff <- HADSxPHQ$'HADS.-.PROMIS.Skala' - HADSxPHQ$'PHQ.-.PROMIS.Skala'

# Find the average difference
mean_diff <- mean(HADSxPHQ$diff)
mean_diff_hadsxphq <- mean_diff

# Find lower 95% confidence interval limits
lower <- mean_diff - 1.96 * sd(HADSxPHQ$diff)

# Find upper 95% confidence interval limits
upper <- mean_diff + 1.96 * sd(HADSxPHQ$diff)



# Create the Bland-Altman Plot
library(ggplot2)

# ... (your existing data and calculations)

# Create Bland-Altman Plot
HADSxPHQ_BA_plot_weighted <- ggplot(HADSxPHQ, aes(x = avg, y = diff)) +
  geom_point(size=1) +
  geom_hline(yintercept = mean_diff, linetype="dashed", lwd=0.5) +
  geom_hline(yintercept = lower, color = "red", linetype="dashed") +
  geom_hline(yintercept = upper, color = "red", linetype="dashed") +
  geom_hline(yintercept = 0, color = "blue") +
  ggtitle("HADSxPHQ") +
  ylab("Difference Between Instruments") +
  xlab("Average") +
  theme_bw() +
  theme(
    text = element_text(size = 8),  
    axis.title = element_text(size = 6),
    axis.text = element_text(size = 8),
    plot.title = element_text(size = 8) 
  ) +
  xlim(40, 80) +
  ylim(-15, 25)

```

### Grid erstellen
```{r }
library(gridExtra)

Blant_plot_weighted <- suppressWarnings({
  BDIxCESD_BA_plot_weighted
  BDIxHADS_BA_plot_weighted 
  BDIxPHQ_BA_plot_weighted
  BDIxPROMIS_BA_plot_weighted
  CESDxHADS_BA_plot_weighted
  CESDxPHQ_BA_plot_weighted
  PHQxPROMIS_BA_plot_weighted
  HADSxPHQ_BA_plot_weighted 

  grid.arrange(BDIxCESD_BA_plot_weighted, BDIxHADS_BA_plot_weighted, BDIxPHQ_BA_plot_weighted, BDIxPROMIS_BA_plot_weighted, CESDxHADS_BA_plot_weighted, CESDxPHQ_BA_plot_weighted, PHQxPROMIS_BA_plot_weighted,HADSxPHQ_BA_plot_weighted, nrow = 2)
})



file_path <- "../04_results/Blant_plot_weighted.png"
ggsave(file_path, Blant_plot_weighted, width = 10, height = 6, units = "in")



```
## Mean diff und sd über alle berrechnen
```{r }
overall_mean <- mean(mean_diff_bdixcesd, mean_diff_bdixhads, mean_diff_bdixphq, mean_diff_bdixpromis, mean_diff_cesdxhads, mean_diff_cesdxphq, mean_diff_phqxpromis, mean_diff_hadsxphq)


sd_bdi_BDIxCESD <- sd(BDIxCESD$`BDI.-.PROMIS.Skala`)
sd_bdi_BDIxHADS <- sd(BDIxHADS$`BDI.-.PROMIS.Skala`)
sd_bdi_BDIxPHQ <- sd(BDIxPHQ$`BDI.-.PROMIS.Skala`)
sd_bdi_BDIxPROMIS <- sd(BDIxPROMIS$`BDI.-.PROMIS.Skala`)

sd_cesd_BDIxCESD <- sd(BDIxCESD$`CESD.-.PROMIS.Skala`)
sd_hads_BDIxHADS <- sd(BDIxHADS$`HADS.-.PROMIS.Skala`)
sd_phq_BDIxPHQ <- sd(BDIxPHQ$`PHQ.-.PROMIS.Skala`)
sd_promis_BDIxPROMIS <- sd(BDIxPROMIS$`PROMIS`)

sd_cesd_CESDxHADS <- sd(CESDxHADS$`CESD.-.PROMIS.Skala`)
sd_cesd_CESDxPHQ <- sd(CESDxPHQ$`CESD.-.PROMIS.Skala`)

sd_hads_CESDxHADS <- sd(CESDxHADS$`HADS.-.PROMIS.Skala`)
sd_phq_CESDxPHQ <- sd(CESDxPHQ$`PHQ.-.PROMIS.Skala`)

sd_phq_PHQxPROMIS <- sd(PHQxPROMIS$`PHQ.-.PROMIS.Skala`)

sd_promis_PHQxPROMIS <- sd(PHQxPROMIS$`PROMIS`)

sd_hads_HADSxPHQ <- sd(HADSxPHQ$`HADS.-.PROMIS.Skala`)

sd_phq_HADSxPHQ <- sd(HADSxPHQ$`PHQ.-.PROMIS.Skala`)

standardabweichungen <- c(
  sd_bdi_BDIxCESD, sd_bdi_BDIxHADS, sd_bdi_BDIxPHQ, sd_bdi_BDIxPROMIS,
  sd_cesd_BDIxCESD, sd_hads_BDIxHADS, sd_phq_BDIxPHQ, sd_promis_BDIxPROMIS,
  sd_cesd_CESDxHADS, sd_cesd_CESDxPHQ,
  sd_hads_CESDxHADS, sd_phq_CESDxPHQ,
  sd_phq_PHQxPROMIS, sd_promis_PHQxPROMIS,
  sd_hads_HADSxPHQ, sd_phq_HADSxPHQ
)

mean_standardabweichungen <- mean(standardabweichungen)

print(mean_standardabweichungen)



```