---
title: "02_script_for_plots"
output: html_document
date: "2024-01-10"
---
# Scatterplots
## load data
```{r, echo=FALSE}
library(readxl)
library(dplyr)
library(openxlsx)

file_path <- "../01_data/SUBSET_BDI.xlsx"
SUBSET_BDI <- read.xlsx(file_path)  %>% unique()

file_path <- "../01_data/SUBSET_CESD.xlsx"
SUBSET_CESD <- read.xlsx(file_path) %>% unique()

file_path <- "../01_data/SUBSET_HADS.xlsx"
SUBSET_HADS <- read.xlsx(file_path) %>% unique()

file_path <- "../01_data/SUBSET_PHQ.xlsx"
SUBSET_PHQ <- read.xlsx(file_path) %>% unique()

file_path <- "../01_data/SUBSET_PROMIS.xlsx"
SUBSET_PROMIS <- read.xlsx(file_path) %>% unique()

```


## Scatter und Bland-Altmann Plots

```{r, echo=FALSE}
library(Hmisc)

BDIxCESD = inner_join(SUBSET_BDI, SUBSET_CESD, by = c("Study", "Variable")) %>% unique()
BDIxHADS <- inner_join(SUBSET_BDI, SUBSET_HADS, by = c("Study", "Variable")) %>%unique()
BDIxPHQ <- inner_join(SUBSET_BDI, SUBSET_PHQ, by = c("Study", "Variable")) %>%unique()
BDIxPROMIS <- inner_join(SUBSET_BDI, SUBSET_PROMIS, by = c("Study", "Variable")) %>%unique()
CESDxHADS <- inner_join(SUBSET_CESD, SUBSET_HADS, by = c("Study", "Variable")) %>%unique()
CESDxPHQ <- inner_join(SUBSET_CESD, SUBSET_PHQ, by = c("Study", "Variable")) %>%unique()
CESDxPROMIS <- inner_join(SUBSET_CESD, SUBSET_PROMIS, by = c("Study", "Variable")) %>%unique()
HADSxPHQ <- inner_join(SUBSET_HADS, SUBSET_PHQ, by = c("Study", "Variable")) %>%unique()
HADSxPROMIS <- inner_join(SUBSET_HADS, SUBSET_PROMIS, by = c("Study", "Variable")) %>%unique()
PHQxPROMIS <- inner_join(SUBSET_PHQ, SUBSET_PROMIS, by = c("Study", "Variable"))%>%unique()


results = list(BDIxCESD, BDIxHADS, BDIxPHQ, 
BDIxPROMIS, CESDxHADS, CESDxPHQ, CESDxPROMIS, HADSxPHQ, 
HADSxPROMIS, PHQxPROMIS)
names(results) =  c("BDIxCESD", "BDIxHADS", "BDIxPHQ", 
"BDIxPROMIS", "CESDxHADS", "CESDxPHQ", "CESDxPROMIS", "HADSxPHQ", 
"HADSxPROMIS", "PHQxPROMIS")

results$BDIxPROMIS$PROMIS_PROMIS.Skala = results$BDIxPROMIS$PROMIS

results2 = lapply(names(results), function(x){
results[[x]]$measure_1 = strsplit(x, "x")[[1]][1]
results[[x]]$measure_2 = strsplit(x, "x")[[1]][2]
results[[x]]$value_1 = results[[x]][, grep("PROMIS", names(results[[x]]))[1]]
results[[x]]$value_2 =  results[[x]][, grep("PROMIS", names(results[[x]]))[2]]
results[[x]]$groupsize = results[[x]][,"groupsize.x"]
results[[x]][, c("Study", "Variable", "measure_1", "measure_2", "value_1", "value_2", "groupsize")]
})

str(results2)
results3 = bind_rows(results2)
library(ggplot2)
results3$groupsize = as.numeric(results3$groupsize)

ggplot(results3, aes(x = value_1, value_2)) + geom_point() + facet_grid(measure_1 ~ measure_2) + geom_abline() + geom_smooth()
ggplot(results3, aes(x = value_1, value_2)) + geom_point(aes(size = groupsize)) + facet_grid(measure_1 ~ measure_2) + geom_abline() 

results3$m = (results3$value_1 + results3$value_2)/2
results3$d = (results3$value_1 - results3$value_2)

ggplot(results3, aes(x = m, y = d)) + geom_point()+ facet_grid(measure_1 ~ measure_2)

results4 = results3 %>% group_by(measure_1, measure_2) %>% summarise(mean1 = mean(d), wgt_mean = wtd.mean(d, w = groupsize, na.rm = T),
                                                                     sd = sd(d), wtd_sd = sqrt(wtd.var(d, w = groupsize)),
                                                                     lo = mean1-1.96*sd, hi = mean1+1.96*sd,
                                                                     wtd_lo = wgt_mean-1.96*wtd_sd, wtd_hi = wgt_mean+1.96*wtd_sd)

ggplot(results3, aes(x = m, y = d)) + geom_point()+ facet_grid(measure_1 ~ measure_2) + 
  geom_hline(data = results4, aes(yintercept = mean1)) + 
  geom_hline(data = results4, aes(yintercept = lo), linetype = 2) +
  geom_hline(data = results4, aes(yintercept = hi), linetype = 2) +
  geom_text(data = results4, aes(x = 30, y = mean1, label = sprintf("%.1f", mean1)), vjust = -.2) +
  geom_text(data = results4, aes(x = 30, y = lo, label = sprintf("%.1f", lo)), vjust = -.2) +
  geom_text(data = results4, aes(x = 30, y = hi, label = sprintf("%.1f", hi)), vjust = -.2) +
  coord_cartesian(xlim = c(20,80)) +
  labs(title = "Unweighted")

ggplot(results3, aes(x = m, y = d)) + geom_point()+ facet_grid(measure_1 ~ measure_2) + 
  geom_hline(data = results4, aes(yintercept = wgt_mean)) + 
  geom_hline(data = results4, aes(yintercept = wtd_lo), linetype = 2) +
  geom_hline(data = results4, aes(yintercept = wtd_hi), linetype = 2) +
  labs(title = "Weighted")


```

```{r, echo=FALSE}

library(ggplot2)

max_groupsize_row <- which.max(results3$groupsize)

# Remove this row to avoid distortion in the plot
results3_adjusted <- results3[-max_groupsize_row, ]

# Generate the plot without the outlier
plot <- ggplot(results3_adjusted, aes(x = groupsize, y = d, group = interaction(d > 0.5), color = d > 0.5)) +
  geom_line() +  # Connect points with lines
  geom_point() +  # Add points to visualize individual observations
  scale_color_manual(values = c("red", "blue"),  # Define custom colors for different categories of 'd'
                     labels = c("d ≤ 0.5", "d > 0.5"),
                     name = "Difference Category") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +  # Dashed line at d = 0.5
  labs(
    x = "Group Size",
    y = "Difference (d)",
    title = "Plot of Difference vs. Group Size",
    subtitle = "Two lines showing trends converging towards d = 0.5",
    caption = "Outlier with very high group size removed for better visualization."
  ) +
  theme_minimal()  # Use a minimalistic theme for a clean plot

# Display the plot
print(plot)

ggsave("plot_of_difference_vs_group_size.png", plot, width = 10, height = 8, dpi = 300)






# Load the ggplot2 library for creating visuals
library(ggplot2)

# Assuming 'results' contains the columns 'd' for differences and 'groupsize' for the size of each group.
# This visualization explores how the difference 'd' varies with 'groupsize', including smooth trend lines.

# Generate the plot
plot <- ggplot(results3, aes(x = groupsize, y = d, color = d > 0.5)) +
  geom_point() +  # Add points to visualize individual observations
  geom_smooth(aes(group = interaction(d > 0.5)),  # Add smooth lines to show trends
              method = "loess",  # 'loess' is good for smaller datasets, use 'gam' for larger datasets
              se = TRUE,  # Display confidence interval around the smooth line
              color = "black") +  # Specify color of the smooth line if desired
  scale_color_manual(values = c("red", "blue"),  # Define custom colors for different categories of 'd'
                     labels = c("d ≤ 0.5", "d > 0.5"),
                     name = "Difference Category") +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "grey") +  # Dashed line at d = 0.5
  labs(
    x = "Group Size",
    y = "Difference (d)",
    title = "Smoothed Plot of Difference vs. Group Size",
    subtitle = "Smooth trends showing convergence towards d = 0.5",
    caption = "Data points are colored based on the category of 'd'. Smooth lines include a confidence interval."
  ) +
  theme_minimal()  # Use a minimalistic theme for a clean plot

# Display the plot
print(plot)


```

## mean of (absolute) d 
```{r, echo=FALSE}

d_absolute <- abs(results3$d)
d_absolute_mean <- mean(d_absolute)
summary(d_absolute)
sd(d_absolute)

#mean of d
d <- results3$d
d_mean <- mean(d)
summary(d)
sd(d)
```

## linear mixed model estimates

Wir möchten die Differenz i in Gruppe j aufteilen in Anteile, die auf Unterschiede der jeweiligen Fragebogenkombination j zurückgehen und Unterschiede die auch innerhalb der Fragebogenkombination noch zwischen einzelnen Studien i bestehen. 

Es ist ein Mixed model weil wir von festen und von random effects (pro Studie unterscheiden sich die Differenzen) ausgehen. 


```{r, echo=FALSE}
#install.packages("lme4")
#install.packages("lmerTest")
#install.packages("Matrix")

library(lme4)
library(sjPlot)

# Erstelle das Intercept-Only-Modell
interceptonlymodel <- lmer(formula = d ~ 1 + (1|Study),
                           weights = groupsize,
                           data = results3)

# Zeige die Zusammenfassung des Modells an
summary(interceptonlymodel)

# Plotte das Modell
#plot_model(model = interceptonlymodel, type = 'pred', terms = 'Study')


```

### Hinzufügen eines Level-1 Prädiktors
Wir wollen herausfinden, woran es liegen könnte, dass die Studien unterschiedliche Differenzen haben.

Hypothese 1: Die Differenz hängt mit der Fragebogenkombination zusammen.


```{r, echo=FALSE}

# install.packages("knitr")
# install.packages("kableExtra")

library(knitr)
library(kableExtra)


results3$questionnaire_pair = paste(results3$measure_1, results3$measure_2)
results3$questionnaire_pair = factor(paste(results3$measure_1, results3$measure_2))

interceptonlymodel <- lmer(formula = d ~ 1 + questionnaire_pair + (1|Study), weights = groupsize, data = results3)
summary(interceptonlymodel)
lmerTest::ls_means(interceptonlymodel, which = "questionnaire_pair")

```

# ANOVA

H0 wird abgelehnt -> es gibt signifikante Unterschiede zwischne den Differenzen der Fragebögen
```{r, echo=FALSE}

anova_result <- aov(d ~ questionnaire_pair, data = results3)
summary(anova_result)

```
# Forest plot 

```{r, echo=FALSE}

## load up the packages we will need: 
library(tidyverse)
library(gt)
library(patchwork)

library(ggplot2)

# Data
data <- data.frame(
  Comparison = c("BDI x CESD (7 studies)", "BDI x HADS (9 studies)", "BDI x PHQ (20 studies)", "BDI x PROMIS (1 study)",
                 "CESD x HADS (14 studies)", "CESD x PHQ (9 studies)", "CESD x PROMIS (1 study)",
                 "HADS x PHQ (19 studies)", "HADS x PROMIS (1 study)", "PHQ x PROMIS (6 studies)"),
  Estimate = c(-2.97582, 1.52532, -0.78826, 1.79057, 2.85519,
               1.46963, 5.45416, -2.47907, -2.65198, 5.30093),
  Std.Error = c(1.31949, 0.97459, 0.68534, 2.98016, 0.82313,
                0.89610, 1.29958, 0.70739, 3.06720, 1.03198),
  lower = c(-5.59149, -0.40445, -2.15921, -4.21102, 1.20904,
            -0.32298, 2.89030, -3.89421, -8.80756, 3.25347),
  upper = c(-0.36015, 3.45508, 0.58269, 7.79216, 4.50134,
            3.26224, 8.01801, -1.06393, 3.50360, 7.34839),
  p.value = c(0.0261462, 0.1202153, 0.2546478, 0.5509542,
               0.0009684, 0.1062524, 4.193e-05, 0.0008742, 0.3912369, 1.388e-06)
)


# Order the data by Estimate
data <- data[order(data$Estimate), ]

# Forest plot
plot <- ggplot(data, aes(x = Estimate, y = Comparison)) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = lower, xmax = upper), height = 0.2) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey") +
  scale_x_continuous(limits = c(-10, 10)) +
  theme_minimal() +
  labs(
    title = "Forest Plot",
    subtitle = "Comparison of Questionnaires",
    x = "Estimate",
    y = "Comparison",
    caption = "Error bars represent 95% confidence intervals"
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )


# Define the file path
file_path <- "../04_results/forest_plot.png"

# Save the plot
ggsave(file_path, plot, width = 10, height = 8)

plot




```

# save table 2
```{r, echo=FALSE}

lmme <- data
lmme$p.value <- ifelse(lmme$p.value < 0.001, "p < 0.001", paste("p =", lmme$p.value))
lmme$Estimate <- round(lmme$Estimate, 2)
lmme$Std.Error <- round(lmme$Std.Error, 2)
lmme$lower <- round(lmme$lower, 2)
lmme$upper <- round(lmme$upper, 2)


#install.packages("writexl")
library(writexl)
file_path <- "../04_results/lmme.xlsx"
write.xlsx(lmme, file_path, rowNames = FALSE)

```

